Comparison of New York codes

### 2015-11-23 024-comparison-NY.Rmd
Rerun analyses

```{r}
ny_codes %>% 
  lapply(function(x) {
    best_section_matches(x, ny_scores, threshold = 0.15) %>% 
      summarize_borrowings()
  })
```

>>>>

```{r}
intra_code_network <- ny_codes %>% 
  lapply(function(x) {
    best_section_matches(x, ny_scores, threshold = 0.15) %>% 
      summarize_borrowings()
  }) %>% 
  bind_rows()
```

```{r}
library("igraph")
g <- intra_code_network %>% 
  select(original_code, match_code, weight = percentage_sections) %>% 
  filter(!is.na(match_code)) %>%
  filter(weight >= 0.02) %>% 
  graph_from_data_frame() %>% 
  add_layout_(with_graphopt()) 
plot(g, edge.width = E(g)$weight * 10)
```
